\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-05-14 doc/sw-system.tex
Replaced 'step' with 'kick' wherever possible - 'step' makes sense when describing the trajectory as a random walk. #207

Suppose the $k+1^{\rm th}$ volunteer now submits a classification, on the same
subject just classified by the $k^{\rm th}$ volunteer. We can generalise
\Eref{eq:app:first} by replacing the prior probability with the current
posterior probability:
\begin{align}
  \label{eq:app:update}
  \pr(\LENS & |C_{k+1},\training_{k+1},\data) = \\
  & \frac{1}{Z} \pr(C_{k+1}|\LENS,\training_{k+1}) \cdot \pr(\LENS|\data) \\ \notag
{\rm where}\;\; Z = & \pr(C_{k+1}|\LENS,\training_{k+1})\cdot\pr(\LENS|\data) \\ \notag
      & + \pr(C_{k+1}|\NOT,\training_{k+1})\cdot\pr(\NOT|\data), \notag
\end{align}
and $\data = \{C_k,\trainingk\}$ is the set of all previous
classifications, and the set of training subjects seen by each of those
volunteers.
$\pr(\LENS|\data)$ is the fundamental property of each test subject that
we are trying to infer. We track $\pr(\LENS|\data)$ as a function of time,
and by comparing it to a lower or upper threshold, make decisions about
whether to retire the subject from the classification interface, or
flag it for further study, respectively.

@@

The progress of the subjects during the online analysis is illustrated in
\Fref{fig:swap:subject-trajectories}. Subjects appear on this plot at the tip of
the arrow, at zero classifications and prior probability; they then drift
downwards as they are classified by the crowd, with each agent applying the
appropriate kick in probability based on what it hears its volunteer say.
Encouragingly, sims (blue) tend to end up with high probability, while duds
(red) pile up at low probability; test subjects (black) mostly drift to low
probability, but some go the other way. The latter will help make up the
candidate sample. As this plot shows, around 10 classifications are typically
required for a subject to reach the retirement (or detection) threshold.

@@

\begin{minipage}{\linewidth}
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0000fgj_gri.pdf}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0000fgj_stage1_trajectory.pdf}
    \end{minipage}
  \end{minipage}\hfill
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0003j2s_gri.pdf}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0003j2s_stage1_trajectory.pdf}
    \end{minipage}
  \end{minipage}
\end{minipage}
\caption{Illustrative examples of
false negatives (blue) and false positives (red) from the classification of
the \SW$-$\cfhtls training set. The trajectory plot for each of the 4 subjects is
shown to the right of its image. Lefthand panels show the most common types of
trajectories: short step random walks resulting from no high skill classifiers
viewing the subject. The righthand panels show examples where higher skill
classifiers have been involved, causing random walks with longer step lengths
(top) and catastrophic mis-classifications (bottom right). Note that both these
subjects were {\it very nearly} detected but didn't quite reach the threshold
set (marked by the blue dashed line). Insets for the false
negatives show the lens feature. The inset for the lower righthand panel shows
where most volunteers believed a lens was located. There is no corresponding inset
for the lower left panel because no particular feature stood out to the
classifiers. Instead, the volunteers clicked many different features.}
\label{fig:discuss:performance:trajectories}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The false positives show similar behaviour, for example in the bottom lefthand
panel of the figure. As well as subjects being ``unlucky'' in this way, there
are two less common failure modes associated with mistakes made by higher skill
volunteers, illustrated in the righthand column of the figure. In the false negative
subject shown in the top right-hand panel, several high skill classifiers update
the subject upwards in log probability by some way each time, but other,
comparable skill classifiers mis-classify the system to lower probability.   The
trajectory looks like a random walk, but with bigger steps; this particular
subject came very close to crossing the detection  threshold three times, but
didn't quite make it. The bottom right-hand panel shows an example of a final,
apparently rare, failure mode: we see some short-step random walk behaviour,
followed by a mis-classification by a very high skill ``expert'' classifier
after 20 classifications that promotes the subject to high probability.

@@

However, identification failures (around 60\%, from inspection of a random sample)
seem to be due to the statistical noise associated with
the many short, semi-random direction steps arising from classifications made by
low skill, inexperienced
classifiers (\Sref{sec:results:crowd}).
While improved training will help reduce this effect, it is here
that targeted task assignment could also help improve system performance, by
bringing higher skill volunteers in when needed. We
advertised \StageTwo of the current project to all registered users; it was
taken up by \StageOne veterans with a broad range of skill, and also picked up a
significant number of new users who did not have enough time to acquire high
skill (since \StageTwo was quite short): of the 1964 volunteers who took part in
the \StageTwo classification round, only 774 were veterans from \StageOne.

>>>>

Suppose the $k+1^{\rm th}$ volunteer now submits a classification, on the same
subject just classified by the $k^{\rm th}$ volunteer. We can generalise
\Eref{eq:app:first} by replacing the prior probability with the current
posterior probability:
\begin{align}
  \label{eq:app:update}
  \pr(\LENS & |C_{k+1},\training_{k+1},\data) = \\
  & \frac{1}{Z} \pr(C_{k+1}|\LENS,\training_{k+1}) \cdot \pr(\LENS|\data) \\ \notag
{\rm where}\;\; Z = & \pr(C_{k+1}|\LENS,\training_{k+1})\cdot\pr(\LENS|\data) \\ \notag
      & + \pr(C_{k+1}|\NOT,\training_{k+1})\cdot\pr(\NOT|\data), \notag
\end{align}
and $\data = \{C_k,\trainingk\}$ is the set of all previous
classifications, and the set of training subjects seen by each of those
volunteers.
$\pr(\LENS|\data)$ is the fundamental property of each test subject that
we are trying to infer. We track $\pr(\LENS|\data)$ as a function of time,
as it is updated;
by comparing it to a lower or upper threshold, we can make decisions about
whether to retire the subject from the classification interface, or
flag it for further study, respectively.

@@

The progress of the subjects during the online analysis is illustrated in
\Fref{fig:swap:subject-trajectories}. Subjects appear on this plot at the tip of
the arrow, at zero classifications and prior probability; they then drift
downwards as they are classified by the crowd, with each agent applying the
appropriate ``kick'' in probability based on what it hears its volunteer say.
Encouragingly, sims (blue) tend to end up with high probability, while duds
(red) pile up at low probability; test subjects (black) mostly drift to low
probability, but some go the other way. The latter will help make up the
candidate sample. As this plot shows, around 10 classifications are typically
required for a subject to reach the retirement (or detection) threshold.

@@

\begin{minipage}{\linewidth}
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0000fgj_gri.pdf}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0000fgj_stage1_trajectory.pdf}
    \end{minipage}
  \end{minipage}\hfill
  \begin{minipage}[t]{0.47\linewidth}
    \begin{minipage}{0.46\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0003j2s_gri.pdf}
    \end{minipage}\hfill
    \begin{minipage}{0.50\linewidth}
      \centering\includegraphics[width=\linewidth]{ASW0003j2s_stage1_trajectory.pdf}
    \end{minipage}
  \end{minipage}
\end{minipage}
\caption{Illustrative examples of
false negatives (blue) and false positives (red) from the classification of
the \SW$-$\cfhtls training set. The trajectory plot for each of the 4 subjects is
shown to the right of its image. Lefthand panels show the most common types of
trajectories: random walks with short steps resulting from no high skill classifiers
viewing the subject. The righthand panels show examples where higher skill
classifiers have been involved, causing larger, more efficient ``kicks''
(top) but also catastrophic mis-classifications (bottom right).
Note that both these
subjects were {\it very nearly} detected but didn't quite reach the threshold
set (marked by the blue dashed line). Insets for the false
negatives show the lens feature. The inset for the lower righthand panel shows
where most volunteers believed a lens was located. There is no corresponding inset
for the lower left panel because no particular feature stood out to the
classifiers. Instead, the volunteers clicked many different features.}
\label{fig:discuss:performance:trajectories}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The false positives show similar behaviour, for example in the bottom lefthand
panel of the figure. As well as subjects being ``unlucky'' in this way, there
are two less common failure modes associated with mistakes made by higher skill
volunteers, illustrated in the righthand column of the figure. In the false negative
subject shown in the top right-hand panel, several high skill classifiers update
the subject upwards in log probability by some way each time, but other,
comparable skill classifiers mis-classify the system to lower probability.   The
trajectory looks like a random walk, but with bigger step sizes; this particular
subject came very close to crossing the detection  threshold three times, but
didn't quite make it. The bottom right-hand panel shows an example of a final,
apparently rare, failure mode: we see some short-step random walk behaviour,
followed by a mis-classification by a very high skill ``expert'' classifier
after 20 classifications that ``kicks'' the subject to high probability.

@@

However, identification failures (around 60\%, from inspection of a random sample)
seem to be due to the statistical noise associated with
the many short, semi-random direction kicks arising from classifications made by
low skill, inexperienced
classifiers (\Sref{sec:results:crowd}).
While improved training will help reduce this effect, it is here
that targeted task assignment could also help improve system performance, by
bringing higher skill volunteers in when needed. We
advertised \StageTwo of the current project to all registered users; it was
taken up by \StageOne veterans with a broad range of skill, and also picked up a
significant number of new users who did not have enough time to acquire high
skill (since \StageTwo was quite short): of the 1964 volunteers who took part in
the \StageTwo classification round, only 774 were veterans from \StageOne.
